\Title

### 2013-02-28 synmut.tex
fig2a little aesthetics

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synonymous polymorphisms in \env, \shankaregion, are mostly deleterious}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We study the dynamics and fate of synonymous mutations more quantitatively by
analyzing data from seven patients from
\citet{shankarappa_consistent_1999,liu_selection_2006} and three patients from
\citet{bunnik_autologous_2008} (patients whose viral population was structured
were excluded from the analysis; see methods and \figurename~S\PCApat).  The
former data set from is restricted to the \shankaregion{} region of \env, while
the data from \citet{bunnik_autologous_2008} covers the majority of \env.
Considering all mutations in a frequency interval $[\nu_0-\delta\nu, \nu_0+\delta\nu]$ at some time
$t$, we calcate the fraction that are still observed at later times $t+\Delta t$. Plotting this fraction against the time interval $\Delta t$, we see that
most synonymous mutations segregate for roughly one year and are lost much more
frequently than expected (panel \ref{fig:fixp1}). The long-time probability of
fixation, $\pfix$, is shown as a function of the
initial frequency $\nu_0$ in panel~\ref{fig:fixp2} (red line). Restricted to the
region \shankaregion, we find that $\pfix$ of synonymous mutations is far below
the neutral expectation.  Outside of \shankaregion, using data from
\citet{bunnik_autologous_2008} only, no such reduction in $\pfix$ is found.
Restricted to the \shankaregion{} region, the sequence samples from
\citet{bunnik_autologous_2008} are fully compatible with data from
\citet{shankarappa_consistent_1999}. The nonsynonymous mutations seem to follow
more or less the neutral expectation (blue line) -- a point to which we will
come back below.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synonymous polymorphisms in \env, \shankaregion, are mostly deleterious}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We study the dynamics and fate of synonymous mutations more quantitatively by
analyzing data from seven patients from
\citet{shankarappa_consistent_1999,liu_selection_2006} and three patients from
\citet{bunnik_autologous_2008} (patients whose viral population was structured
were excluded from the analysis; see methods and \figurename~S\PCApat).  The
former data set from is restricted to the \shankaregion{} region of \env, while
the data from \citet{bunnik_autologous_2008} covers the majority of \env.
Considering all mutations in a frequency interval $[\nu_0-\delta\nu, \nu_0+\delta\nu]$ at some time
$t$, we calculate the fraction that are still observed at later times $t+\Delta t$. Plotting this fraction against the time interval $\Delta t$, we see that
most synonymous mutations segregate for roughly one year and are lost much more
frequently than expected (panel \ref{fig:fixp1}). The long-time probability of
fixation, $\pfix$, is shown as a function of the
initial frequency $\nu_0$ in panel~\ref{fig:fixp2} (red line). Restricted to the
region \shankaregion, we find that $\pfix$ of synonymous mutations is far below
the neutral expectation.  Outside of \shankaregion, using data from
\citet{bunnik_autologous_2008} only, no such reduction in $\pfix$ is found.
Restricted to the \shankaregion{} region, the sequence samples from
\citet{bunnik_autologous_2008} are fully compatible with data from
\citet{shankarappa_consistent_1999}. The nonsynonymous mutations seem to follow
more or less the neutral expectation (blue line) -- a point to which we will
come back below.
